A pandemic-scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-09-30 latex/main.tex
Updates from Overleaf

\subsection{Analysis of deletion events}
\label{sec:supplement_dels}
[TODO This is too terse and too vague. Be concrete and precise. WHICH 
deletions are we talking about?]

@@

However, the placement of several major deletion events
in the ARG differs from the phylogenetic placement of
the corresponding deletion events suggested
in Akaishi and Fujiwara \cite{Akaishi2023}.
That study \cite{Akaishi2023} suggests that
a 6-base deletion at 21,765 occurred
before the divergence of Alpha and Omicron,
but in the ARG this deletion appears to be recurrent,
occurring above the origin nodes of Alpha, BA.1, and BA.4.
Similarly, that study \cite{Akaishi2023} suggests that
a 1-base deletion at 28,271 occurred
before the divergence of Alpha, Delta, and Omicron,
but it is mapped as a recurrent deletion in the ARG
(at the Alpha origin node and above node 1436808).
These differences suggest that
some key deletions carry important phylogenetic signals
ignored by the HMM used by sc2ts.

@@

\begin{figure}
\centering
\centering
\includegraphics[width=\linewidth]{tanglegram_base_tree.pdf}
\caption{
Tanglegram comparing phylogenetic backbones of sc2ts and UShER.
}
\label{fig:tanglegram_base}
\end{figure}

>>>>

\subsection{Analysis of deletion events}
\label{sec:supplement_dels}
% [TODO This is too terse and too vague.
% Be concrete and precise.
%WHICH deletions are we talking about?]

@@

However, the placement of several major deletion events
in the ARG differs from the phylogenetic placement of
the corresponding deletion events suggested
in Akaishi and Fujiwara \cite{Akaishi2023}.
That study \cite{Akaishi2023} suggests that
a 6-base deletion at 21,765 occurred
before the divergence of Alpha and Omicron,
but in the ARG this deletion appears to be recurrent,
occurring above the origin nodes of Alpha, BA.1, and BA.4.
Similarly, that study \cite{Akaishi2023} suggests that
a 1-base deletion at 28,271 occurred
before the divergence of Alpha, Delta, and Omicron,
but it is mapped as a recurrent deletion in the ARG
(at the Alpha origin node and above node 1436808).

@@

\begin{figure}
\centering
\centering
\includegraphics[width=\linewidth]{tanglegram_base_tree.pdf}
\caption{
Tanglegram comparing the basic phylogenetic backbones of sc2ts and UShER.
}
\label{fig:tanglegram_base}
\end{figure}
